Practice Problems

### 2023-09-29 Stats Rethinking/Ch8/Practice Problems.qmd
Update Practice Problems.qmd
Added Lahman Analysis folder and documents

```{r}
m8.5 <- quap(
  alist(
    blooms_std ~ dnorm(mu, sigma),
    mu <- bw*water_cent + bs*shade_cent + bws*water_cent*shade_cent,
    a ~ dnorm(0.5, 0.25),
    bw ~ dnorm(0, 0.25),
    bs ~ dnorm(0, 0.25),
    bws ~ dnorm(0, 0.25),
    sigma ~ dexp(1)
  ), data=d
)

@@

@@

>>>>

```{r}
m8.5 <- quap(
  alist(
    blooms_std ~ dnorm(mu, sigma),
    mu <- a + bw*water_cent + bs*shade_cent + bws*water_cent*shade_cent,
    a ~ dnorm(0.5, 0.25),
    bw ~ dnorm(0, 0.25),
    bs ~ dnorm(0, 0.25),
    bws ~ dnorm(0, 0.25),
    sigma ~ dexp(1)
  ), data=d
)

@@

How do you make a index variable?

```{r}
#We'll make a bed into an integer
d <- d %>% 
  mutate(bed_id = as.integer(bed), .after=bed)
```

```{r}
#Recreate the m8.4 from chapter
m8.4 <- quap(
  alist(
    blooms_std ~ dnorm(mu, sigma),
    mu <- a + bw*water_cent + bs*shade_cent,
    a ~ dnorm(0.5, 0.25),
    bw ~ dnorm(0, 0.25),
    bs ~ dnorm(0, 0.25),
    sigma ~ dexp(1)
  ), data=d
)
```

```{r}
m8h1 <- quap(
  alist(
    blooms_std ~ dnorm(mu, sigma),
    mu <- a[bed_id] + bw*water_cent + bs*shade_cent,
    a[bed_id] ~ dnorm(0.5, 0.25),
    bw ~ dnorm(0, 0.25),
    bs ~ dnorm(0, 0.25),
    sigma ~ dexp(1)
  ), data=d
)
```

```{r}
precis(m8h1, depth=2)
```

```{r}
precis(m8.4)
```

@@

```{r}
compare(m8h1, m8.4, m8.5, func=WAIC)
```

```{r}
plot(compare(m8h1, m8.4, m8.5, func=WAIC))
```
